Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-18 2_SSL_EES/article/article_supplementary.tex
updated interviewees table

The number of die per wafer $D$ depends on the total usable wafer area. The usable area depends on the wafer diameter, the cutting street width between the chips and the exclusion zone at the rim of the wafer.

\begin{equation}
	A_{\text{usable}}=A_{\text{wafer}}-A_{\text{cut}}-A_{\text{exclusion}}
\end{equation}

Determining the usable wafer area as a of these three parameters requires a numerical solution. However, following discussions in literature \cite{de2005investigation}, we approximate the number of good die per wafer as

@@

Devices may be damaged or otherwise rendered unusable during the manufacturing process. The ratio between the number of good devices per step and the number of handled devices per step is known as the yield. Optimizing this yield is critical for reducing manufacturing cost \cite{Kumar2006}. This is because cumulative yield quickly drops as the yield from manufacturing steps with below 100\% yield is multiplied. We must thus consider not only the manufacturing cost per process step, but also the cost including the yield \cite{becker2001use}\cite{becker2001using}. While there are different mathematical approaches to including yield, we follow the definition in  \cite{becker2001use}. We write for the yielded cost $C_{Y_i}$ of a step $i$

@@

>>>>

The number of die per wafer $D$ depends on the total USAble wafer area. The USAble area depends on the wafer diameter, the cutting street width between the chips and the exclusion zone at the rim of the wafer.

\begin{equation}
	A_{\text{USAble}}=A_{\text{wafer}}-A_{\text{cut}}-A_{\text{exclusion}}
\end{equation}

Determining the USAble wafer area as a of these three parameters requires a numerical solution. However, following discussions in literature \cite{de2005investigation}, we approximate the number of good die per wafer as

@@

Devices may be damaged or otherwise rendered unUSAble during the manufacturing process. The ratio between the number of good devices per step and the number of handled devices per step is known as the yield. Optimizing this yield is critical for reducing manufacturing cost \cite{Kumar2006}. This is because cumulative yield quickly drops as the yield from manufacturing steps with below 100\% yield is multiplied. We must thus consider not only the manufacturing cost per process step, but also the cost including the yield \cite{becker2001use}\cite{becker2001using}. While there are different mathematical approaches to including yield, we follow the definition in  \cite{becker2001use}. We write for the yielded cost $C_{Y_i}$ of a step $i$

@@

\section{Anonymized List of Interviewees}

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        \# & sector & role & country & expertise \\ \hline
        1 & academia & sr. researcher & UK & epitaxy \\ \hline
        2 & industry & consultant, form. sr. researcher & USA & device architecture \\ \hline
        3 & industry & consultant, form. head of R\&D & Germany & epitaxy \\ \hline
        4 & academia & professor & Austria & phosphors \\ \hline
        5 & industry & consultant, form. head of R\&D & USA & device architecture \\ \hline
        6 & consulting & consultant, form. sr. technical advisor & USA & device architecture \\ \hline
        7 & academia & professor & Germany & phosphors \\ \hline
        8 & government & R\&D manager & USA & device architecture \\ \hline
        9 & consulting & consultant & USA & device applications \\ \hline
        10 & academia & professor & France & device physics \\ \hline
        11 & industry & sr scientist, form. head of R\&D & USA & device architecture \\ \hline
        12 & industry & principal scientist & Germany & phosphors \\ \hline
        13 & industry & form. head of R\&D & USA & phosphors \\ \hline
    \end{tabular}
    \label{tab:interviews}
    \caption{list of domain experts with whom semi-structured interviews were conducted. \\ Abbreviations: form. - former, sr. - senior}
\end{table}
